---
title: "Project 1 158"
author: "Tesfa Asmara and Kevin Loun"
date: "2/20/2022"
output:
  pdf_document:
    extra_dependencies: ["float"]
bibliography: references.bib
---
```{r, include=FALSE}
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)    # alternatively, this also loads %>%
library(tidyverse)
library(janitor)
library(ggridges)
library(ggplot2)
library(skimr)
knitr::opts_chunk$set(fig.pos="H", out.extra="")
lol10 <- read_csv('training_data.csv')
lol10 <- clean_names(lol10)

```


The dataset for this project contains 10,000 League of Legends ranked matches from the North American region with 775 variables offered through the Riot Games API, provided on Kaggle [@riot][@james_2020]. Each match is pulled from players who rank Gold in the League system, a ranking system that matches players of a similar skill level to play with and against each other. Amongst North American players, the Gold skill level was the second most common tier, achieved by 27.7 percent of players, or approximately 49.86 million players when considered against Riot Games' player base of 180 million [@statista_2021][@riot_tweet]. This dataset will be referred to as $\texttt{lol10}$.

For this project, the following variables are of interest: lane, champion, map side, first summoner spell, kills, deaths, gold earned, and total damage dealt. A figure including all the relevant variables and their description is attached at the end.

We consider the following research question: Does the amount of gold earned have an effect on the total damage dealt for the average Gold-ranked player on the blue team? We want to describe the relationship between the gold earned and the total damage dealt on the blue team in the $\texttt{lol10}$ dataset using a line. We will use the gold earned across all summoners on the blue team as the predictor variable, $x$, to predict the total damage dealt across all summoners on the blue team, $y$. In Figure \@ref(fig:xyplot), we observe the linearity of the regression model, albiet with some curvature. In Figure \@ref(fig:residyhatplot), we observe the nonconstancy of the error terms.

```{r xyplot,fig.height = 3, fig.width = 4, fig.cap = "A scatterplot showing gold earned against total damage dealt on the blue team for 10,000 Gold-ranked matches",echo=FALSE}
lol10 <- lol10 %>%
  mutate(b_total_damage_dealt = b_summoner1_total_damage_dealt + b_summoner2_total_damage_dealt + b_summoner3_total_damage_dealt + b_summoner4_total_damage_dealt + b_summoner5_total_damage_dealt)

lol10 <- lol10 %>%
  mutate(b_gold_earned = b_summoner1_gold_earned + b_summoner2_gold_earned + b_summoner3_gold_earned + b_summoner4_gold_earned + b_summoner5_gold_earned)

lol10 %>%
  ggplot(aes(x=b_gold_earned,y=b_total_damage_dealt))+
  geom_point()+
  labs(x = "Gold Earned", y="Total Damage Dealt")
```

```{r residyhatplot,fig.height = 3, fig.width = 4, fig.cap = "Residual plot for the model predicting total damage dealt from gold earned on the blue team for 10,000 Gold-ranked matches.",echo=FALSE}
lolmodel <- lm(b_gold_earned ~ b_total_damage_dealt, data = lol10)
lolmodel %>%
  ggplot(aes(x=lolmodel$fitted.values ,y= lolmodel$residuals))+
  geom_point()+
  labs(x = "Predicted values of total damage dealt", y="Residuals") + geom_hline(yintercept=0, linetype="dashed", color = "red")
```

Next, we consider $H_0$. In this instance, we have: $H_0:\beta_1 = 0$ and $H_a:\beta_1 \neq 0.$ The 95% confidence interval for $\beta_1$ is $(0.066,0.067)$; this means that we are 95% confident that $\beta_1$ is in this range. Since the confidence interval for $\beta_1$ does not contain 0, it can be concluded that there is evidence of a linear relationship between the gold earned and the total damage dealt for the blue team.

```{r,echo=FALSE, results='hide'}
confint(lolmodel)
```


| Variable 	| Description 	|
|---	|---	|
| b_summoner1_role 	| The role of summoner 1 on the blue side of the map, taking on the values of TOP_LANE, MID_LANE, BOT_LANE, or JUNGLE. 	|
| b_summoner2_role 	| The role of summoner 2 on the blue side of the map, taking on the values of TOP_LANE, MID_LANE, BOT_LANE, or JUNGLE. 	|
| b_summoner3_role 	| The role of summoner 3 on the blue side of the map, taking on the values of TOP_LANE, MID_LANE, BOT_LANE, or JUNGLE. 	|
| b_summoner4_role 	| The role of summoner 4 on the blue side of the map, taking on the values of TOP_LANE, MID_LANE, BOT_LANE, or JUNGLE. 	|
| b_summoner5_role 	| The role of summoner 5 on the blue side of the map, taking on the values of TOP_LANE, MID_LANE, BOT_LANE, or JUNGLE. 	|
| b_summoner1_championId 	| A number corresponding to the champion of summoner 1 on the blue side of the map. 	|
| b_summoner2_championId 	| A number corresponding to the champion of summoner 2 on the blue side of the map. 	|
| b_summoner3_championId 	| A number corresponding to the champion of summoner 3 on the blue side of the map. 	|
| b_summoner4_championId 	| A number corresponding to the champion of summoner 4 on the blue side of the map. 	|
| b_summoner5_championId 	| A number corresponding to the champion of summoner 5 on the blue side of the map. 	|
| b_summoner1_championId 	| A number corresponding to the first spell of summoner 1 on the blue side of the map. 	|
| b_summoner2_championId 	| A number corresponding to the first spell of summoner 2 on the blue side of the map. 	|
| b_summoner3_championId 	| A number corresponding to the first spell of summoner 3 on the blue side of the map. 	|
| b_summoner4_championId 	| A number corresponding to the first spell of summoner 4 on the blue side of the map. 	|
| b_summoner5_championId 	| A number corresponding to the first spell of summoner 5 on the blue side of the map. 	|
| b_summoner1_kills 	| The number of kills obtained by summoner 1 on the blue side of the map. 	|
| b_summoner2_kills 	| The number of kills obtained by summoner 2 on the blue side of the map. 	|
| b_summoner3_kills 	| The number of kills obtained by summoner 3 on the blue side of the map. 	|
| b_summoner4_kills 	| The number of kills obtained by summoner 4 on the blue side of the map. 	|
| b_summoner5_kills 	| The number of kills obtained by summoner 5 on the blue side of the map. 	|
| b_summoner1_deaths 	| The number of deaths obtained by summoner 1 on the blue side of the map. 	|
| b_summoner2_deaths 	| The number of deaths obtained by summoner 2 on the blue side of the map. 	|
| b_summoner3_deaths 	| The number of deaths obtained by summoner 3 on the blue side of the map. 	|
| b_summoner4_deaths 	| The number of deaths obtained by summoner 4 on the blue side of the map. 	|
| b_summoner5_deaths 	| The number of deaths obtained by summoner 5 on the blue side of the map. 	|
| b_summoner1_gold_earned 	| The gold obtained by summoner 1 on the blue side of the map. 	|
| b_summoner2_gold_earned 	| The gold obtained by summoner 2 on the blue side of the map. 	|
| b_summoner3_gold_earned 	| The gold obtained by summoner 3 on the blue side of the map. 	|
| b_summoner4_gold_earned 	| The gold obtained by summoner 4 on the blue side of the map. 	|
| b_summoner5_gold_earned 	| The gold obtained by summoner 5 on the blue side of the map. 	|
| b_summoner1_total_damage_dealt 	| The total damage dealt by summoner 1 on the blue side of the map. 	|
| b_summoner2_total_damage_dealt 	| The total damage dealt by summoner 2 on the blue side of the map. 	|
| b_summoner3_total_damage_dealt 	| The total damage dealt by summoner 3 on the blue side of the map. 	|
| b_summoner4_total_damage_dealt 	| The total damage dealt by summoner 4 on the blue side of the map. 	|
| b_summoner5_total_damage_dealt 	| The total damage dealt by summoner 5 on the blue side of the map. 	|
| r_summoner1_role 	| The role of summoner 1 on the red side of the map, taking on the values of TOP_LANE, MID_LANE, BOT_LANE, or JUNGLE. 	|
| r_summoner2_role 	| The role of summoner 2 on the red side of the map, taking on the values of TOP_LANE, MID_LANE, BOT_LANE, or JUNGLE. 	|
| r_summoner3_role 	| The role of summoner 3 on the red side of the map, taking on the values of TOP_LANE, MID_LANE, BOT_LANE, or JUNGLE 	|
| r_summoner4_role 	| The role of summoner 4 on the red side of the map, taking on the values of TOP_LANE, MID_LANE, BOT_LANE, or JUNGLE. 	|
| r_summoner5_role 	| The role of summoner 5 on the red side of the map, taking on the values of TOP_LANE, MID_LANE, BOT_LANE, or JUNGLE. 	|
| r_summoner1_championId 	| A number corresponding to the champion of summoner 1 on the red side of the map. 	|
| r_summoner2_championId 	| A number corresponding to the champion of summoner 2 on the red side of the map. 	|
| r_summoner3_championId 	| A number corresponding to the champion of summoner 3 on the red side of the map. 	|
| r_summoner4_championId 	| A number corresponding to the champion of summoner 4 on the red side of the map. 	|
| r_summoner5_championId 	| A number corresponding to the champion of summoner 5 on the red side of the map. 	|
| r_summoner1_championId 	| A number corresponding to the first spell of summoner 1 on the red side of the map. 	|
| r_summoner2_championId 	| A number corresponding to the first spell of summoner 2 on the red side of the map. 	|
| r_summoner3_championId 	| A number corresponding to the first spell of summoner 3 on the red side of the map. 	|
| r_summoner4_championId 	| A number corresponding to the first spell of summoner 4 on the red side of the map. 	|
| r_summoner5_championId 	| A number corresponding to the first spell of summoner 5 on the red side of the map. 	|
| r_summoner1_kills 	| The number of kills obtained by summoner 1 on the red side of the map. 	|
| r_summoner2_kills 	| The number of kills obtained by summoner 2 on the red side of the map. 	|
| r_summoner3_kills 	| The number of kills obtained by summoner 3 on the red side of the map. 	|
| r_summoner4_kills 	| The number of kills obtained by summoner 4 on the red side of the map. 	|
| r_summoner5_kills 	| The number of kills obtained by summoner 5 on the red side of the map. 	|
| r_summoner1_deaths 	| The number of deaths obtained by summoner 1 on the red side of the map. 	|
| r_summoner2_deaths 	| The number of deaths obtained by summoner 2 on the red side of the map. 	|
| r_summoner3_deaths 	| The number of deaths obtained by summoner 3 on the red side of the map. 	|
| r_summoner4_deaths 	| The number of deaths obtained by summoner 4 on the red side of the map. 	|
| r_summoner5_deaths 	| The number of deaths obtained by summoner 5 on the red side of the map. 	|
| r_summoner1_gold_earned 	| The gold obtained by summoner 1 on the red side of the map. 	|
| r_summoner2_gold_earned 	| The gold obtained by summoner 2 on the red side of the map. 	|
| r_summoner3_gold_earned 	| The gold obtained by summoner 3 on the red side of the map. 	|
| r_summoner4_gold_earned 	| The gold obtained by summoner 4 on the red side of the map. 	|
| r_summoner5_gold_earned 	| The gold obtained by summoner 5 on the red side of the map. 	|
| r_summoner1_total_damage_dealt 	| The total damage dealt by summoner 1 on the red side of the map. 	|
| r_summoner2_total_damage_dealt 	| The total damage dealt by summoner 2 on the red side of the map. 	|
| r_summoner3_total_damage_dealt 	| The total damage dealt by summoner 3 on the red side of the map. 	|
| r_summoner4_total_damage_dealt 	| The total damage dealt by summoner 4 on the red side of the map. 	|
| r_summoner5_total_damage_dealt 	| The total damage dealt by summoner 5 on the red side of the map. 	|
: Variables and their descriptions